\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-10 Thesis.tex
just the conclusion

\begin{wrapfigure}{c}{\textwidth}
\vspace{-30pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo}
    } 
\vspace{-20pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagoreanFull}
\vspace{0pt}
  \end{center}
\end{wrapfigure}

@@

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-16pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
    } 
\vspace{-20pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

@@

Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations. By improving the creation user interface and allowing for users to choose their own designs, it becomes more easy to use and more attractive for users. Adding an editor would make this much more user friendly for creators as well. To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\

@@

Overall it is even thinkable to create a different version of this system that could be made available to common users outside this research domain. The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves. Possibly the system could even suggest dependencies. As an example, I could very well envision a biology presentation that explains Photosynthesis and allows the attentive student to catch up on processes that transform ADP to ATP.\\

@@

This whole research project would also benefit from machine learning which could allow us to make smart offers of likely dependencies. On an individual basis we could use it to learn what the user knows and what the user does not know. Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn. Combining machine learning with the identification of more didactic paths or figures within the data could further improve knowledge transfer.

>>>>

\begin{wrapfigure}{c}{\textwidth}
\vspace{-30pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}
    } 
\vspace{-20pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagoreanFull}
\vspace{0pt}
  \end{center}
\end{wrapfigure}

@@

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-16pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.87\textwidth]{assets/final/fullPresentation2}
    } 
\vspace{-20pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

@@

Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations. By improving the creation user interface and allowing for users to choose their own designs, it becomes more easy to use and more attractive for users. Adding an editor would make this more user friendly for creators as well. To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\

@@

Overall it is even thinkable to create a different version of this system that could be made available to common users outside this research domain. The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves. Possibly the system could even suggest dependencies. As an example, I could very well envision a biology presentation that explains photosynthesis and allows the attentive student to catch up on dependencies such as the process that transforms ADP to ATP.\\

@@

This whole research project might also benefit from machine learning which could allow us to make smart offers of likely dependencies. On an individual basis we could use it to learn what the user knows and what the user does not know. Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn. Combining machine learning with the identification of more didactic paths or figures within the data such as the example in \autoref{fig:pathExample} could further improve knowledge transfer.
